### 2019-05-24 reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

We have added four new implementations to Task Bench: Dask, bulk synchronous MPI,
MPI+OpenMP and MPI+CUDA. Results are included in the evaluation
section, including preliminary results from experiments with GPUs on
the Piz Daint supercomputer.

Major changes in the revised paper:

  * New implementations: Dask, bulk synchronous MPI, MPI+OpenMP and MPI+CUDA
  * New sections:
      - Implementation: Sections 4.3 (Dask) and 4.5 (MPI+X)
      - Evaluation: Section 5.9 (GPU experiment)
  * New figures:
      - Listings 1 and 2 (code samples)
      - Figure 15 (GPU experiment)
  * Updated Figures 3 and 4 (see also lines 300-312)
  * Updated Section 7 with insights derived from Task Bench

### 2019-05-24 0_abstract.tex
Apply comments by Sean.

\begin{abstract}
% 147 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench lowers the barrier to benchmarking multiple systems by making
the implementation for a given system orthogonal to the benchmarks
themselves: all benchmarks constructed with Task Bench automatically
run on all Task Bench implementations, and vice versa. Furthermore,
Task Bench's parameterization allows a wide variety of benchmark
scenarios that distill the key characteristics of larger applications.

>>>>

\begin{abstract}
% 148 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench lowers the barrier to benchmarking multiple programming systems by making
the implementation for a given system orthogonal to the benchmarks
themselves: all benchmarks constructed with Task Bench automatically
run on all Task Bench implementations, and vice versa. Furthermore,
Task Bench's parameterization allows a wide variety of benchmark
scenarios that distill the key characteristics of larger applications.
